{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-14 bmvc_review.tex
Table Updated

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Metric/Method & $R_{t}^{L}$+$R_{t}^{S}$+$R_{s}$ ({\it E}nKCF) & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & LCT \cite{ma2015long}\\
\hline\hline
Precision ($20$px) & \textbf{54.5} & 48.09 & & & &\\
Success Rate ($50\%$) & \textbf{40.2} & 36.04 & & & & \\
Frame Per Second & \textbf{416} & 370 & & & & \\
\hline
\end{tabular}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.}
\end{table}

>>>>

\begin{table}
\small
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Metric/Method & $R_{t}^{L}$+$R_{t}^{S}$+$R_{s}$ ({\it E}nKCF) & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & LCT \cite{ma2015long}\\
\hline\hline
Precision ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 51.88 & 51.29 & 52.14 \\
Success Rate ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 35.12 & 34.42 & 38.51\\
Frame Per Second & \textbf{416} & 370 & 425 & 367 & 490 & 151 \\
\hline
\end{tabular}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF. $R_{t}^{S}$ and $R_{s}$ are used as proposed in
\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used to perform realistic comparison. In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).} 
\end{table}
